Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-13 longoutput.tex
Do more work on longoutput

Let $C$ undergo the above two transforms so it has the following properties
\begin{itemize}
	\item All states are real (including initial, intermediate states, and output).
	\item Consists of only Hadamard and Toffoli gates
	\item The last $\gamma$ of the gates are all identity gates (can easily achieve by padding)
\end{itemize}

@@

We then attempt to construct a local Hamiltonian with ground state that encodes the history of the computation: $$\phi=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
We do so by ensuring states perpendicular to it have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification is taken from \cite{PhysRevA.78.012352}.

First, we ensure that the invalid clock states have high eigenvalues by applying the following Hamiltonian to the time register.
$$H_{clock}=\sum_{t=1}^{T-1}\ket{01}\bra{01}_{t,t+1}$$
Note that $H_{clock}\in\spn\mathcal{G}_{XZ}$
$$H_{clock}=\frac{1}{4}(Z_1 - Z_T) + \frac{1}{4}\sum_{t=1}^{T-1}(I-Z_tZ_{t+1}) $$
This can be checked by fixing the first and last qubit, then doing induction on the number of switches.

@@

TODO
Now we combine the three Hamiltonians defined. First consider their kernels.
$$K_{clock}=\ker H_{clock}$$
$$K_{in}=\ker H_{in}$$
$$K_{prop}=\ker H_{prop}$$

It is

@@

Given $\ket\phi$, now we're interested in the value of $\braket{\phi|H|\phi}$. Here we follow \cite{PhysRevA.93.022326}.

@@

Take $p_0$ and $p_1$ to be the probability to measure $\sgn(d_S)\braket{\phi|S|\phi}=-1$ on $\ket\psi$ and $\ket\phi$ respectively, where $\phi$ is perpendicular to $\psi$. Obviously, $p_0=\frac{1}{2}$, and $p_1<\frac{1}{2}$... TODO Now what? Hypothesis testing...?

>>>>

Let $C$ undergo the above transformations so it has the following properties
\begin{itemize}
	\item All states are real (including initial, intermediate states, and output).
	\item Consists of only Hadamard and Toffoli gates
	\item The last $\gamma$ of the gates are all identity gates (can easily achieve by padding)
\end{itemize}

@@

We then attempt to construct a local Hamiltonian with ground state that encodes the history of the computation: $$\psi_{circuit}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
We do so by ensuring states perpendicular to it have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification is taken from \cite{PhysRevA.78.012352}.

First, we ensure that the invalid clock states have high eigenvalues by applying the following Hamiltonian to the time register.
$$H_{clock}=\sum_{t=1}^{T-1}\ket{01}\bra{01}_{t,t+1}$$
As it is a sum of projections, $H_{clock}\geq 0$. We also show that $H_{clock}\in\spn\mathcal{G}_{XZ}$.
$$H_{clock}=\frac{1}{4}(Z_1 - Z_T) + \frac{1}{4}\sum_{t=1}^{T-1}(I-Z_tZ_{t+1}) $$
This can be checked by fixing the first and last qubit, then doing induction on the number of switches.

@@

Now we combine the three Hamiltonians defined. First consider their kernels.
$$K_{clock}=\ker H_{clock}$$
$$K_{in}=\ker H_{in}$$
$$K_{prop}=\ker H_{prop}$$
Notice that (TODO need proof or no?)
$$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\psi_{circuit}}$$
We now define
$$K=(\spn\set{\psi_{circuit}})^\bot$$
and consider $H_{clock}\big|_K,H_{in}\big|_K,H_{prop}\big|_K$. That is, we restrict the following computations to the subspace $K$. We apply the projection lemma.
$$\exists J_{clock},
\lambda(H_{in}\big|_K+J_{clock}H_{clock}\big|_K)\geq
\lambda(H_{in}\big|_{K\cap K_{clock}})-\frac{1}{8}$$
$$\exists J_{prop},
\lambda(H_{in}\big|_K+J_{clock}H_{clock}\big|_K+J_{prop}H_{prop}\big|_K)\geq
\lambda(H_{in}\big|_{K\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_K)\geq\frac{3}{4}$$
So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$. It has the following properties.
\begin{itemize}
	\item $\braket{\psi_{circuit}|H_{circuit}|\psi_{circuit}}=0$
	\item $\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$ for $\ket\phi$ such that $\braket{\phi|\psi_{circuit}}=0$
	\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$
\end{itemize}

@@

Given $\ket\phi$, now we're interested in the value of $\braket{\phi|H|\phi}$. Here we follow \cite{PhysRevA.93.022326}. Note that if $\phi=\psi_{circuit}$, then $\braket{\phi|H|\phi}=0$. If $\braket{\phi|\psi_{circuit}}=0$, then $\braket{\phi|H|\phi}>\beta>\frac{1}{\poly(T)}$.

@@

Take $p_0$ and $p_1$ to be the probability to measure $\sgn(d_S)\braket{\phi|S|\phi}=-1$ on $\ket\psi_{circuit}$ and $\ket\phi$ respectively, where $\phi$ is perpendicular to $\psi_{circuit}$. Obviously, $p_0=\frac{1}{2}$, and $p_1<\frac{1}{2}$... TODO Now what? Hypothesis testing...?
